Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-04 manuscript/manuscript.Rmd
Added code for empirical gof statistics in the appendix

```
```{r include = FALSE, eval = FALSE}
data <- .get_test_statistic_data(manuscript_dir = manuscript_dir)

@@

>>>>

```{r include = FALSE, eval = FALSE}
data <- .get_test_statistics_data(manuscript_dir = manuscript_dir)

@@

# Appendix D: Generalisability of empirical goodness of fit test

Add details on how generalisable the test statistic is for fits generated by other methods:

- using different estimation method (Cramér-von Mises)
- using conventional power transformation
- using non-robust power transformation (only outlier-free data)

```{r}
data <- .get_test_statistics_data_appendix(manuscript_dir = manuscript_dir)
